ms_figures

### 2018-10-16 man/ms_figures.Rmd
update

## Figure 1 Location map 
- [X] La figura 1 puede tener un mapa de localización de SN, otro de las poblaciones de roble (clasificadas por colores: cluster; y señalando las dos poblaciones muestradas en dendro). Ver MIGRAME dataset.

    - [] Ver https://github.com/ajpelu/qpyr_dendro/blob/master/out/fig/geomap/mapa_situacion.pdf 
    - Ojo con los nombres SJ (Que hacemos?)

## Figure 2. Plot de anomalias
- [X] Solamente Anomalias estandarizadas

## Figure 3. 
")
```

**Figure 1**. Distribution of *Quercus pyrenaica* forests in Iberian Peninsula (a) and in Sierra Nevada mountain (b). Different colours indicate oak population cluster's identified in Sierra Nevada [@PerezLuque2015]. For each population, a grid with the MODIS pixels is shown (see material and methods). Detailed location of the dendroecological sampling sites: northern (San Juan, SJ) (c), and southern ones (Cáñar: CA-Low and CA-High) (d). Colour orthophotography of 2009 from Regional Ministry of the Environment, Regional Government of Andalusia.

@@

# Lm CA-High
dfcaH <- cro_sites %>% 
  filter(year >= 1975) %>% 
  filter(site == 'CA-High')

mCaH <- lm(bai_mean ~ year, dfCaH)
# summary(m1)
r2caH <- format(summary(mCaH)$r.squared, digits = 3)

@@

mCaL <- lm(bai_mean ~ year, dfCaL)
r2caL <- format(summary(mCaL)$r.squared, digits = 3)

@@

mSJ <- lm(bai_mean ~ year, dfSJ)
r2SJ <- format(summary(mSJ)$r.squared, digits = 3)

**Figure 4.** Basal Area Increment (BAI) chronologies of *Q. pyrenaica* for northern population (SJ; *green*) and southern ones: low-elevation (CA-Low; *pink*) and high-elevation (CA-High, *purple*) sites. Shading areas coorespond to standard error of the mean. Number of series are displayed in the upper plot. We only show chronologies with # trees > 5. Linear trend since 1975 is shown for southern high-elevation site (CA-High) ($r_2$ = `r r2caH`).

>>>>

- [] Figure 1. Location map

    - [] Ver https://github.com/ajpelu/qpyr_dendro/blob/master/out/fig/geomap/mapa_situacion.pdf

- [] Figure 2. Plot de anomalias
- [] Figure 3. Resilience metrics
- [] Figure 4. BAI chronologies

")
```

**Figure 1**. Distribution of *Quercus pyrenaica* forests in the Iberian Peninsula (a) and in Sierra Nevada mountain range (b). Different colours indicate oak population cluster's identified in Sierra Nevada [@PerezLuque2015]. For each population, a grid with the MODIS pixels is shown (see material and methods). Detailed location of the dendroecological sampling sites: northern (San Juan, SJ) (c), and southern ones (Cáñar: CA-Low and CA-High) (d). Colour orthophotography of 2009 from Regional Ministry of the Environment [@IECA2009].

@@

# To get p.value of the model 
# https://stackoverflow.com/questions/5587676/pull-out-p-values-and-r-squared-from-a-linear-regression
lmp <- function(modelobject) {
    if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
    f <- summary(modelobject)$fstatistic
    p <- pf(f[1],f[2],f[3],lower.tail=F)
    attributes(p) <- NULL
    return(p)
}

# Lm CA-High
dfCaH <- cro_sites %>% 
  filter(year >= 1975) %>% 
  filter(site == 'CA-High')

mCaH <- lm(bai_mean ~ year, dfCaH)
summary(mCaH)
r2caH <- format(summary(mCaH)$r.squared, digits = 3)
pCaH <- lmp(mCaH)

@@

mCaL <- lm(bai_mean ~ year, dfCaL)
summary(mCaL)
r2caL <- format(summary(mCaL)$r.squared, digits = 3)
pCaL <- lmp(mCaL)

@@

mSJ <- lm(bai_mean ~ year, dfSJ)
summary(mSJ)
r2SJ <- format(summary(mSJ)$r.squared, digits = 3)
pSJ <- lmp(mSJ)
```

**Figure 4.** Basal Area Increment (BAI) chronologies of *Q. pyrenaica* for northern population (SJ; *green*) and southern ones: low-elevation (CA-Low; *pink*) and high-elevation (CA-High, *purple*) sites. Shading areas correspond to standard error of the mean. Number of series are displayed in the upper plot. We only show years replicated with # series > 5. Linear trend since 1975 is shown for southern high-elevation site (CA-High) ($r_2$ = `r r2caH`).
